\documentclass[onecolumn,amsmath,aps,fleqn, superscriptaddress]{revtex4}
 
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epsfig}
\usepackage{subfigure}
\usepackage{mathrsfs}
\usepackage{longtable}
\usepackage{enumerate} 
\usepackage{multirow}
\usepackage{color}

\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    citecolor = {MidnightBlue},
    linkcolor = {BrickRed},
    urlcolor = {BrickRed}
}

\newcommand{\be}{\begin{eqnarray}}
\newcommand{\ee}{\end{eqnarray}}

\allowdisplaybreaks[1]
 
\begin{document}

\title{Constraining IA with shape-measurement methods: $n_{\rm eff}$ / shape noise term issue}

\author{Danielle Leonard}

\maketitle

{\it Here are some notes summarizing the issue we discussed in our meeting yesterday, August 23, 2017.}

\vspace{2mm}

For a given observational scenario, we have $n_{\rm eff}$, the effective surface density of source galaxies. This is $1/{\rm arcmin}^2$ for SDSS and $26/{\rm arcmin}^2$ for LSST. This value refers to the effective surface density of sources for the full sample of source galaxies, without any cuts (e.g. on photometric redshift).

However, we are concenred with source samples which are defined by cuts on photometric redshifts, so we need to calculate their $n_{\rm eff}^\prime$ values from the known values for the full source samples.

Previously, I was getting $n_{\rm eff}^\prime$ from $n_{\rm eff}$ using this expression:
\begin{equation}
n_{\rm eff}^\prime = n_{\rm eff} \frac{\int_{z_p^{min}}^{z_p^{max}} dz_p \tilde{w}(z_p) \frac{dN}{dz_p}}{\int_{0}^{\infty} dz_p \tilde{w}(z_p) \frac{dN}{dz_p}}
\label{neff_prev}
\end{equation} 
where $z_p^{min}$ and $z_p^{max}$ are the lower and upper photo-z cuts on the source sample, and $\tilde{w}$ are the weights, given by:
\begin{equation}
\tilde{w}(z_p) = \frac{1}{\Sigma_c^2(z_l, z_p)(\sigma_\gamma^2 + \sigma_e^2)}
\label{weights}
\end{equation}
Note that I have assumed $z_l$ is a fixed single value for now as we did yesterday to simplify the equations.

The problem with equation \ref{neff_prev} is that $\tilde{w}(z_p)$ is definitionally zero for $z_p$ below $z_l$, so 
$n_{\rm eff}^\prime = n_{\rm eff}$ for any value of $z_p^{min}$ such that $0\le z_p^{\rm min}\le z_l$. This is clearly wrong, since such a source sample does not include sources below $z_p^{\rm min}$, which in general exist and contribute to the calculation of $n_{\rm eff}$.

What I am currently doing is the following. First, get a source-sample-appropriate value of $n_{\rm eff}^\prime$ via:
\begin{equation}
n_{\rm eff}^\prime = n_{\rm eff} \frac{\int_{z_p^{min}}^{z_p^{max}} dz_p \frac{dN}{dz_p}}{\int_{0}^{\infty} dz_p \frac{dN}{dz_p}}
\end{equation}
My logic here is that $n_{\rm eff}$ by definition only differs from a `non-effective' surface density in that it acounts for measurement error $\sigma_e$, and we are modelling $\sigma_e$ as z-independent. I'm not sure if this logic is sound so please tell me if it doesn't make sense to you.

Given then $n_{\rm eff}^\prime$, we still have to account for the factor of $\Sigma_c^{-2}$ in the weights. I'm suggesting that the shape-noise term of the covariance matrix is given by:
\begin{equation}
\frac{\sigma_{\gamma}^2}{n_{\rm eff}^\prime n_l} \frac{\int_{z_p^{min}}^{z_p^{max}} dz_p \Sigma_c^{2}(z_l, z_p) \frac{dN}{dz_p}}{\int_{z_p^{min}}^{z_p^{max}}  dz_p  \frac{dN}{dz_p}}
\label{first}
\end{equation}
where I've left out the factors of area that turn $n_{\rm eff}^\prime n_l$ into a number of lens-source pairs.

In practice this will diverge as $z_p$ goes to $z_l$, so actually what I'm doing is: 
 \begin{equation}
\frac{\sigma_{\gamma}^2}{n_{\rm eff}^\prime n_l} \frac{\int_{z_p^{min}}^{z_p^{max}} dz_p \Sigma_c^{-2}(z_l, z_p) \frac{dN}{dz_p}}{\left(\int_{z_p^{min}}^{z_p^{max}} dz_p \Sigma_c^{-2}(z_l, z_p) \frac{dN}{dz_p}\right)^2} 
 \end{equation}
 This method makes some sense to me for the following reason. Our weights here are inverse-variance weights, which I think is equivalent to saying that the variance is the inverse of a sum over weights. We can write the inverse of a sum over weights as:
 \begin{equation}
\frac{\left(\sigma_{\gamma}^2 + \sigma_e^2\right)}{n_s^\prime n_l} \frac{\int_{z_p^{min}}^{z_p^{max}} dz_p \Sigma_c^{2}(z_l, z_p) \frac{dN}{dz_p}}{\int_{z_p^{min}}^{z_p^{max}}  dz_p  \frac{dN}{dz_p}}
 \end{equation}
 where $n_s^\prime$ is the non-effective surface density of sources.
 
 My understanding is that going from $n_s^\prime$ to $n_{\rm eff}^\prime$ somehow accounts for the measurement noise $\sigma_e$, so then changing to $n_{\rm eff}^\prime$, an inverse sum over weights is given by equation \ref{first}.
 
 Let me know if this makes sense and, if not, where you think I might be going wrong.
 
%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------

\end{document}
